Full Brain Blood-Oxygen-Level-Dependent Signal \\ Parameter Estimation using Sequential Monte Carlo Methods

### 2010-08-20 doc/presentation/main.tex
some changes to presentation

\documentclass{beamer}
\usepackage[orientation=landscape,size=custom,width=16,height=10,scale=0.5,debug]{beamerposter}

\mode<presentation>
{
  \usetheme{VT}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

\usefonttheme[onlylarge]{structurebold}
\usecolortheme{crane}
\setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
\setbeamertemplate{navigation symbols}{}
\setbeamercovered{transparent}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{graphics}
%\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage[small]{caption}
\usepackage{algorithmic}

\title{BOLD Parameter Estimation using Sequential Monte Carlo Methods}

@@

\author{Micah Chambers}

\institute {Virginia Tech Bioimaging Systems Lab}

@@

\section{FMRI Review}
\begin{frame}{The BOLD Response}
\begin{figure}
\includegraphics[scale=.23]{model}
\caption{
    \tiny
    \cite{nonlinearfiltering}
}
\end{figure}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage[orientation=landscape,size=custom,width=16,height=10,scale=0.5]{beamerposter}

\mode<presentation>
{
  \usetheme{Antibes}
  % or ...

  %\setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

%\usefonttheme[onlylarge]{structurebold}
%\usecolortheme{crane}
%\setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
%\setbeamertemplate{navigation symbols}{}
%\setbeamercovered{transparent}

\usepackage{graphics}
%\usepackage{times}
%\usepackage[T1]{fontenc}
%\usepackage[small]{caption}
\usepackage{algorithmic}

\title{Full Brain Blood-Oxygen-Level-Dependent Signal \\
Parameter Estimation using Sequential Monte Carlo Methods}

@@

\author{Micah Chambers}
\institute{Virginia Tech Bioimaging Systems Lab}

@@

\section{Background}
\begin{frame}{The BOLD Response}
\begin{figure}
\includegraphics[scale=.23]{model}
\caption{
    \tiny
    \cite{nonlinearfiltering}
}
\end{figure}
\end{frame}
